---
title: "Alcohol vs Seat choice"
author: "Kelly Acevedo"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

# Introduction 

Our data provided is from the UCDavis which is the amount of alcohol consumed per week different seating rows

$B_0$: There is no difference in the average amount of alcohol consumed per week base on seating row.

$H_A$:The average of the number drinks is different between at least two rows. 

#Methods
We are trying to predict the alcohol consumption based on the seating rows

Data :

alcohol ~ Seat
alcohol is a numerical variable
seat is a categorical variable

So we use the numerical~cat file.
#Description
#Graphical Description 

```{r}
boxplot(alcohol~Seat,data=davisdata)
```
This shows that there is a significant difference in the back rows consumption of alcohol compared to the middle and back rows in other words the box plot, students in the back row seem to be consuming more alcohol. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The table shows that the back row has a mean of 9.6 and the front row has a mean of 1.8,also that the middle row has a mean of 3.2. So this shows that students in the back row tend to drink more.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

This shows that the P-value is 0.000116 which means that the students in all the rows don't consume the same amount of alcohol. 


```{r}
plot(TukeyHSD(model1))
```

Bases on the Tukey HSD test we determined that people seated in the back row drink more than people drinking in the middle and front rows. There is change in alcohol consumption between the middle and front rows. 

## Conclusions

We tried to determined what kind of  difference in students who consume alcohol in rows 1, 2, 3 are.So, the p-value is 0.000116 which is less than 0.05 and it  means that we reject the null hypothesis. Once we analized the graph given to us.We can say that students in the back row drink more alcohol than the middle and front row.
